MFCCs, Chroma Features, and Spectrogram Images for Deepfake Audio Classification Using Machine Learning

### 2024-12-06 paper/ieeepaper.tex
updated paper headings and mentions reflecting prof meeting
added future work

\subsubsection{VGG16}
Nora TODO
\subsubsection{ResNet50}
Nora TODO

\subsection{Support Vector Machine (SVM)}

@@

\subsection{Gradient Boosting}

@@

@@

\section{Future Work}
Nora TODO
\section{Conclusion}

>>>>

@@

@@

Prof said we need to mention a bit about what algorithms we used here as well as discussing results

@@

\section{Future Work}
Several methods were explored to identify deepfake audio using machine learning; however, despite our promising results, more investigation is needed to compare the impact of chroma features on multiple algorithms besides SVM. We would also like to work on improving the accuracy of all approaches on the \textit{for-2sec} and \textit{for-rerec} datasets. Lastly, it could be meaningful to explore other audio representations other than MFCCs and Mel-Spectrograms to consider features which these representations may not encompass.

\section{Conclusion}
